---
title: "Synthetic Sales Script Documentation"
author: "Waseem"
output: html_document
---

AI Assistance Declaration: I used ChatGPT (GPT-5.6 Sol) for Markdown structure, writing assistance, layout suggestions, and revision support on October 2, 2026. Prompts used are documented in Appendix.md. I manually reviewed the generated Markdown structure and content for clarity, consistency, and syntax. No external or personal dataset was provided to the AI. I am responsible for the accuracy and originality of this work.

# Purpose

This R Markdown document explains a small R example that creates and displays a **synthetic monthly sales dataset**. The data are fictional and are used only to demonstrate clear R project documentation.

The example has three tasks:

1. create the synthetic dataset;
2. display and summarize the data; and
3. create a simple visualization.

## Inputs

There are no external files or real datasets.

The only input is a manually defined synthetic data frame containing:

- `Month` - six fictional monthly labels;
- `Sales` - six fictional sales values.

## Create the Synthetic Data

The following R code creates the dataset.

```{r create-data}
sales_data <- data.frame(
  Month = c("January", "February", "March", "April", "May", "June"),
  Sales = c(120, 145, 138, 160, 172, 185)
)

sales_data
```

## Inspect the Data

The structure of the data can be checked with `str()`.

```{r inspect-data}
str(sales_data)
```

A basic summary of the synthetic sales values can be produced with `summary()`.

```{r summarize-data}
summary(sales_data$Sales)
```

## Visualization

The following code creates a bar chart using base R.

```{r plot-data}
barplot(
  sales_data$Sales,
  names.arg = sales_data$Month,
  main = "Synthetic Monthly Sales",
  xlab = "Month",
  ylab = "Sales"
)
```

## Outputs

When the document is run or knitted, the expected outputs are:

- a table containing six rows of synthetic data;
- the R structure of the data frame;
- a summary of the synthetic `Sales` values; and
- a bar chart of sales by month.

## Validation

I reviewed the document to make sure:

- Markdown headings are organized consistently;
- R code uses fenced R Markdown chunks;
- each code chunk has a descriptive label;
- the purpose, inputs, and outputs are clearly separated;
- no personal or real-world dataset is used; and
- the document can be previewed or knitted in RStudio.

Before final submission, I will knit or preview this `.Rmd` file in RStudio and confirm that all sections and code chunks render correctly.

## AI Assistance Disclosure

I used ChatGPT (GPT-5.6 Sol) on October 2, 2026 for suggestions on document organization, Markdown formatting, code-block presentation, and wording. The prompts and key responses are documented in `Appendix.md`. I reviewed the final structure and syntax and remain responsible for the submitted work.
